Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-06 doc/main_jfm.tex
some changes (fig,ref)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations.
\todo[inline]{Need a reference here}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$. The red curves are the
  midplanes. Inter-monolayer slip is observed by comparing the relative
  locations of the blue and yellow particles.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
  parabolic flow where the strength of the flow is
  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
  is $w=25$~nm. The configuration occurs when $t=10000$. The inset plots
  the trajectory of mean $y$-position over time.}
\end{figure}

@@

We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape. The reduced area $A^*$ of the starting JP vesicle is closed to 1 and $A^*=0.9$ at the equilibrium
state. A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}. An interesting outcome is that the mean
$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
may be caused by the granularity of the JP vesicle and choices of model parameters.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations. (\cite{Zgorski2019,denOtter2007})
\todo[inline]{Need a reference here}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$ which correspond to $0\ \mu $s, $2.44\ \mu $s, and $4.88\ \mu $s. The red curves are the midplanes. Inter-monolayer slip is observed by comparing the relative  locations of the blue and yellow particles.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
  parabolic flow where the strength of the flow is
  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
  is $w=25$~nm. The configuration occurs when $t=6.1\ \mu$s and red arrows indicate the tank-treading motion. The inset plots the trajectory of mean $y$-position over time.}
\end{figure}

@@

We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape. The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium
state. A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}. An interesting outcome is that the mean
$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
may be caused by the granularity of the JP vesicle and choices of model parameters.
